Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields

### 2014-04-08 dictionary.tex
having problems
back on track now
Thinking about the structure of dictionary.

%%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%
\title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}
\date{\today}
\author{Clifton Cunningham}
\email{cunning@math.ucalgary.ca}
\address{University of Calgary}
\author{David Roe}
\email{roed.math@gmail.com}
\address{Pacific Institute for the Mathematical Sciences, University of Calgary}
\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
\keywords{sheaf--function dictionary, geometrization, quasicharacter sheaves, commutative group schemes}

@@

Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
Motivated by ...., in this paper we ... The component group of the Neron model of algebraic torus over local field ...   The sheaf--function dictionary for etale group schemes is significantly different . . .\todo{Needs a new front end to really set the tone, heighten the contrast to the connected case and point to applications.}

@@

\subsection*{Application}

In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
The ability to work with non-connected group schemes,
of which the component group of the special fibre of the Neron model of a torus is an important example,
plays a crucial role in this application,
since these group schemes are not connected in general.
This process of creating a category from the group of quasicharacters of such a torus
informs our choice of the term \emph{quasicharacter sheaf} here.

We also want to situate our teminology in a historical context.
Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
see for example, \cite{kamgarpour:09a}.
As explained above, quasicharacter sheaves evolved from this notion,
with an eye toward quasicharacters of $p$-adic groups.
However, the main use of the term character sheaf is of course due to Lusztig.
It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
over algebraically closed fields with finite cyclic component groups in the series of papers
beginning with \cite{lusztig:disconnected1}.
When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves.

@@

\section{Preliminary definitions}\label{sec:QCschemes}

@@

\section{Quasicharacter sheaves}\label{sec:category}

@@

\section{Trace of Frobenius}\label{sec:Frob}

@@

\section{Invisible quasicharacter sheaves}\label{sec:invisible}

@@

\section{Pull-back and products}\label{sec:pullback}

@@

\section{Base change}\label{sec:basechange}

@@

\section{Bounded quasicharacter sheaves}\label{sec:bounded}

@@

\section{Finite quasicharacter sheaves}\label{sec:finite}

@@

@@

\section{Group Cohomology}

>>>>

%%%%%%%%%%%%%%%%%% HEADING %%%%%%%%%%%%%%%%%%

\title[Lost in Translation: The function--sheaf dictionary]{Lost in Translation: \\ The function--sheaf dictionary for smooth commutative group schemes over finite fields}

\date{\today}
\author{Clifton Cunningham}
\email{cunning@math.ucalgary.ca}
\address{University of Calgary}
\author{David Roe}
\email{roed.math@gmail.com}
\address{Pacific Institute for the Mathematical Sciences, University of Calgary}
\subjclass[2010]{14F05 (primary), 14L15 (secondary)}
\keywords{sheaf--function dictionary, geometrization, quasicharacter sheaves, commutative group schemes}

@@

@@

\subsection*{Motivation and Application}

Our interest in the function--sheaf dictionary for smooth commutative group schemes over $\Fq$, especially etale commutative group schemes, comes from an application to $p$-adic representation theory.
In \cite{cunningham-roe:13a} we consider quasicharacter sheaves on the
Greenberg transform of the N\'eron model of an algebraic torus over an arbitrary local field.
The ability to work with non-connected group schemes,
of which the component group of the special fibre of the Neron model of a torus is an important example,
plays a crucial role in this application,
since these group schemes are not connected in general.
This process of creating a category from the group of quasicharacters of such a torus
informs our choice of the term \emph{quasicharacter sheaf} here.

\subsection*{Comparison with other character sheaves}

We also want to situate our terminology in a historical context.
Some people refer to local systems satisfying \eqref{introbox} on a connected, commutative algebraic group as character sheaves;
see for example, \cite{kamgarpour:09a}.
As explained above, quasicharacter sheaves evolved from this notion,
with an eye toward quasicharacters of $p$-adic groups.
However, the main use of the term character sheaf is of course due to Lusztig.
It is applied to certain perverse sheaves on connected reductive algebraic groups over algebraically closed fields in
\cite{lusztig:85a}*{Def.~2.10} and to certain perverse sheaves on reductive groups
over algebraically closed fields with finite cyclic component groups in the series of papers
beginning with \cite{lusztig:disconnected1}.
When commutative, such groups are extensions of $\ZZ/n\ZZ$ by a torus,
in which case it is not difficult to relate Frobenius-stable character sheaves to our quasicharacter sheaves. 
In particular, all quasicharacter sheaves on such groups are visible.

@@

\section{Quasicharacter sheaves}

\subsection{Definitions}\label{sec:QCschemes}

@@

%\subsection{Main definition}\label{sec:category}

@@

\subsection{Trace of Frobenius}\label{sec:Frob}

@@

\subsection{Invisible quasicharacter sheaves}\label{sec:invisible}

@@

\subsection{Pull-back and products}\label{sec:pullback}

@@

\subsection{Base change}\label{sec:basechange}

@@

\section{Bounded and Finite quasicharacter sheaves}%\label{sec:bounded}

\subsection{Bounded quasicharacter sheaves}\label{sec:bounded}

@@

\subsection{Finite quasicharacter sheaves}\label{sec:finite}

@@

\subsection{Definition, revisited}

@@

\subsection{Group Cohomology}
